\section{Introduction}
\subsection{Goal - TODO upon scope is resolved}
The goal of this project is to build a deep learning model that tackles the challenge laid out in the ``Google Landmark Recognition and Retrieval Challenge", which revolves around helping users remember their past trips by classifying/labeling different landmarks from around the world. After the recognition aspect, the second part (if there is time) would be to perform retrieval, i.e. given a query of a particular image, we would output images with the same landmark. These tasks involve designing, building, and training an image recognition model to effectively perform the recognition task required to a competitive degree.
\subsection{Problem Definition}
We seek to train a neural net that will classify an image of a landmark to the appropriate landmark. For example, when the following image of the TODO EIFFEL TOWER is passed to the neural network, it should output a high probability that the correct class is EIFFEL TOWER.

During preprocessing, we resize the input image. So, images $X$ passed to the this classifier lie within $L: \mathbb{R}^{NxNx3}$ TODO . There are $K$ classes of landmarks in our dataset, so our function $f$ outputs probabilities $Y \in [0,1]^K$. Our objective is to maximize the probability that the correct landmark class is one of the top 5 landmark classes predicted by our network: $P(IN-TOP-5(f(X),Y)$. We felt that this objective is appropriate as there may be more than one landmark in an image.
\subsection{Data}
To control data storage costs, we used a subset of the over 1 million urls and 15,000 landmark classes provided by the contest organizers to train our network. To obtain the data, we wrote a script to download these images and resize them to TODO size. In total, our training set of TODO images is 43GB in size and our test set of TODO images is 5GB in size. 

The data we are provided with is in the form of URLs, from which we can write a script to retrieve the actual images. While this project seems similar to ILSVRC in that we are also classifying images (recognition and retrieval), in this project, there are over 15,000 classes (as opposed to 1,000 in ILSVRC), and the number of training examples per class may not be very large. Nevertheless, the data comes from Google images, and the expanded data set contains over 1 million images. In the test data, each image can contain one landmark, no landmark or multiple landmarks.